\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rishi Kumar} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{mailto:rsi.dev17@gmail.com}{rsi.dev17@gmail.com} \\ West Bengal, IN} 
\address{\href{https://rishikumar.dev}{https://rishikumar.dev} \\ \href{https://linkedin.com/in/rsidev}{linkedin.com/in/rsidev} \\ \href{https://www.github.com/k3yss}{https://www.github.com/k3yss}}  %

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	OBJECTIVE
	%	\begin{rSection}{OBJECTIVE}

	%	{Software Engineer with 2+ years of experience in XXX, seeking full-time XXX roles.}


	%	\end{rSection}
	%----------------------------------------------------------------------------------------
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Education}
		
		{\bf Indian Institute of Information Technology}  \hfill {Kalyani, West Bengal}\\
		B.Tech Compter Science \hfill {Dec 2021 - June 2025}\\
		Secretary Free and Open Source Club, Freescape 
		
		{\bf Chinmaya Vidyalaya, Bokaro}  \hfill {Bokaro, Jharkhand}\\
		Senior Secondary School \hfill {2018 - 2020} \\
		%Minor in Linguistics \smallskip \\
		Received a Gold Medal for scoring the highest marks in computer science
		%Member of Upsilon Pi Epsilon \\
		
	\end{rSection}
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{WORK EXPERIENCE}
		
		\textbf{Google Summer Of Code 2023} \hfill Remote\\
		KDE \hfill \textit{May 2023 - September 2023}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Managed to write X\% growth for XYZ using A, B, and C skills.
			\item Led the whole world XYZ which led to X\% of improvement in ABC
			\item Developed XYZ that did A, B, and C using X, Y, and Z. 
		\end{itemize}
		
		\textbf{Role Name} \hfill Jan 2017 - Jan 2019\\
		Company Name \hfill \textit{San Francisco, CA}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Achieved X\% growth for XYZ using A, B, and C skills.
			\item Led XYZ which led to X\% of improvement in ABC
			\item Developed XYZ that did A, B, and C using X, Y, and Z. 
		\end{itemize}
		
	\end{rSection} 
	
	%----------------------------------------------------------------------------------------
	% TECHINICAL STRENGTHS	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{SKILLS}
		
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Programming Languages: & C/C++, Javascript, Python, Go\\
			Frameworks: & Qt(QtQuick, QML), React, NextJS \\
			Tools: & Git, Linux, Docker, Github Actions\\
		\end{tabular}\\
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	PROJECTS SECTION
	%----------------------------------------------------------------------------------------

	\begin{rSection}{PROJECTS}
		\vspace{-1.25em}
		\item \textbf{Hiring Search Tool.} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
		\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
		\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
	\end{rSection} 

	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Extra-Curricular Activities} 
		\begin{itemize}
			\item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
			\item	Sample bullet point.
		\end{itemize}
		
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Leadership} 
		\begin{itemize}
			\item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
		\end{itemize}
		
		
	\end{rSection}
	
	
\end{document}
